Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-30 paper/paper-DrexelFormat.tex
updated paper - done

\section{Machine Learning with Driving Data}\label{sec:MLDD}

@@

\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The evidence of this can be found during training LSTM in both models. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:mae_accuracy} show the accuracy of the result from LSTM on each iterations during training. Figure \ref{fig:sae_loss} and Figure \ref{fig:mae_loss} show the loss (error) on each iterations during training.

@@

Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accuracy 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%). It implies that the data fed to LSTM had noise or problems. It also means that AE in {\em second model} and {\em third model} did not work correctly. The next subsection covers more detailed explanation about the error from AE in {\em second model} and {\em third model}.

>>>>

\section{Machine Learning with Driving Data}\label{sec:MLDD}
People are concerned about driving behavior for safety.  Human driving behavior has been researched for long time. For example, Macadam illustrates the manual creation of control models showing aspects of human driving behavior on \cite{markkula2012review}.

Many research for human driving behavior use machine learning approach. For example, the paper \cite{ontanon2014case} introduces case-based and instance-based learning for driving behavior. Also the paper \cite{nechyba1998stochastic} applies Hidden Markov Models introduced on \cite{rabiner1986introduction} to develop a similarity measure of control models. The approach is able to measure similarity between driving data from different drivers.

@@

\subsection{Analysis Training LSTM in {\em second model} and {\em third model}}
The difference between {\em first model} and other models is that other models have AE. Therefore, AE layer from {\em second model} and {\em third model} caused worse performance. The evidence of this can be found during training LSTM in both models. Following six figures help to visualize it. Figure \ref{fig:human_accuracy} and Figure \ref{fig:human_loss} respectively show the accuracy and loss from LSTM of {\em first model} on each iterations during training. Figure \ref{fig:sae_accuracy} and Figure \ref{fig:sae_loss} respectively show the accuracy and loss from LSTM of {\em second model} on each iterations during training. Figure \ref{fig:mae_accuracy} and Figure \ref{fig:mae_loss} respectively show the accuracy and loss from LSTM of {\em third model} on each iterations during training.

@@

Training LSTM in {\em second model} and {\em third model} were slow and most cases did not reach accuracy 1 (100\%) while the training LSTM in {\em first model} easily reached accuracy 1 (100\%). Also loss of {\em second model} and {\em third model} did not close to 0. The {\em third model} gave increasing loss when it was trained more. It implies that the data fed to LSTM had noise or problems. It also means that AE in {\em second model} and {\em third model} did not work correctly. The next subsection covers more detailed explanation about the error from AE in {\em second model} and {\em third model}.

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/result_pictures/Human_Accuracy.png}
    \caption{Human Training Accuracy}
    \label{fig:human_accuracy}
\end{figure}

\begin{figure}[t!]
    \centering
    \includegraphics[width=\textwidth]{pictures/result_pictures/Human_Loss.png}
    \caption{Human Training Loss}
    \label{fig:human_loss}
\end{figure}
